Efficient Machine Learning in a Memristor Network

### 2025-03-31 paper/paper.tex
Radius base1

\subsection{Training a Voltage Divider}

@@

Twos

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
    \caption{}\label{fig:evolution_targets}
\end{figure}

\cleardoublepage

\subsection{Training a more general network}

>>>>

\subsection{Training a Memristor Voltage Divider}

@@

In order to investigate the adaptability of the system, we tested it with a set of three consequent desired voltages $V_D=\{1V, 3V, 4V\}$. In \cref{fig:evolution_targets} we show how the output voltgage $V_2$ subsequently adapts to the desired voltages during the training of the pressures in the nodes, the evolution of which can be seen in \cref{fig:evolution_targets}. It is evident that the system can be retrained at any stage to a new desired objective making it reusable. Any other weight type can be chosen, depending on the necessity.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{plots/voltage_divider/evolution_targets.pdf}
    \caption{(a) The trainiang of a memristor voltage divider to a set of desired voltage outputs $V_D = {1V, 3V, 4V}$, indicated by dashed light purple lines. The output voltage $V_2$, indicated by dark purple dots, adapts to the desired output during the training. The input voltages $V_1$ and $V_3$ are constant at $5V$ and $0V$ respectively. (b) The dots with different shades of gray show the values of pressures, chosen as weights, imposed on the three nodes during training.}\label{fig:evolution_targets}
\end{figure}

\subsection{Training a memristor network}

To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies. Physically, reaching a desired input-output voltage mapping in a general electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
